---
title: "Testing `TVVARSS`"
author: "Lucas Nell"
date: "`r format(Sys.Date())`"
output: github_document
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(comment = NA, error = TRUE, echo = FALSE)
library(GenSA)
load('./initial_testing_files/TVVARSS.ml_testing.RData')
```


This document outlines the results of the following:

1. Using optimization and simulated annealing on `TVVARSS.ml` and `cpp_TVVARSS_ml`. The
code to conduct these tests is in 
[this file](./initial_testing_files/TVVARSS.ml_testing.R).
2. Overall output from `TVVARSS` and `cpp_TVVARSS`. The
code to conduct these tests is in 
[this file](./initial_testing_files/TVVARSS_testing.R).

Comparisons between R and C++ versions used the `all.equal` function, which tests for
'near equality'. The tolerance for near equality is 
$`r signif(sqrt(.Machine$double.eps),3)`$.


# Optimization and simulated annealing

## Optimization

#### Using `optim(..., method = 'Nelder-Mead')`

```{r}
summary_output(R_optim[['NM']], Rcpp_optim[['NM']], tv.ml_t[1:3])
```


#### Using `optim(..., method = 'BFGS')`

```{r}
summary_output(R_optim[['BF']], Rcpp_optim[['BF']], tv.ml_t[4:6])
```


#### Using `bobyqa(...)`

```{r}
summary_output(R_optim[['bq']], Rcpp_optim[['bq']], tv.ml_t[7:9])
```


## Simulated annealing

```{r}
summary_output(R_GenSA, Rcpp_GenSA, tv.ml_t[10:12])
```



# Overall output from `TVVARSS` and `cpp_TVVARSS`

Methods `'Nelder-Mead'`, `'BFGS'`, and `'bobyqa'` were run, with and without simulated
annealing, to see how output and performance compared. 
Times below are for the 6 total runs for each version of `TVVARSS`:

```{r}
source('./initial_testing_files/TVVARSS_forC_17Dec16.R')
load('./initial_testing_files/TVVARSS_testing.RData')
cat(paste(
    sprintf('R version took %s minutes',
            round(as.numeric(tv_t[3] - tv_t[2], units = 'mins'), 2)),
    sprintf('cpp version took %s minutes',
            round(as.numeric(tv_t[2] - tv_t[1], units = 'mins'), 2)),
    sep = '\n'))
```


## Using `method = 'Nelder-Mead'`
#### With annealing
```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['Nelder-Mead']]$anneal, R_out[['Nelder-Mead']]$anneal),
          collapse = '\n'),
    sep = '\n'))
```
#### No annealing
```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['Nelder-Mead']]$no_anneal, R_out[['Nelder-Mead']]$no_anneal),
    collapse = '\n'),
    sep = '\n'))
```


## Using `method = 'BFGS'`
#### With annealing

```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['BFGS']]$anneal, R_out[['BFGS']]$anneal),
    collapse = '\n'),
    sep = '\n'))
```
R and C++ versions had output all within $`r signif(sqrt(.Machine$double.eps),3)`$
of each other.

#### No annealing
```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['BFGS']]$no_anneal, R_out[['BFGS']]$no_anneal),
    collapse = '\n'),
    sep = '\n'))
```
This looks weird because the R version here had an error, so returned `NULL`.
Below is the error returned and the output from `traceback()` run afterward::
```{r}
# Error message pasted from running the following:
# e_run <- TVVARSS(X, Tsamplefract = 0.9, method = 'BFGS', show.fig = FALSE, 
#                  annealing = FALSE)
cat(paste('Error in solve.default(FF) : 
  system is computationally singular: reciprocal condition number = 3.97576e-17\n\n'))
# Pasted output from `traceback()`
cat(paste('6: solve.default(FF)
5: solve(FF) at TVVARSS_forC_17Dec16.R#82
4: fn(par, ...)
3: (function (par) 
   fn(par, ...))(c(2442101.41194779, -3417820.0737009, -1299053.23694122, 
   3731843.14805551, -17889292.6552748, -3290188.25617733, 4547907.20822766, 
   -1474431.03066228, 270.996097653055, 1307468.69164327, 95126.5692356095, 
   -3088894.64420066, -3443284.04369214, 4977648.28422679, 150664.747666296, 
   1821492.68435145))
2: optim(fn = TVVARSS.ml, par = par, X = tX, U = tU, par.fixed = par.fixed, 
       method = "BFGS", control = optim.control) at TVVARSS_forC_17Dec16.R#420
1: TVVARSS(X, Tsamplefract = 0.9, method = "BFGS", show.fig = FALSE, 
       annealing = FALSE)'))
```


## Using `method = 'bobyqa'`
#### With annealing
```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['bobyqa']]$anneal, R_out[['bobyqa']]$anneal),
    collapse = '\n'),
    sep = '\n'))
```
#### No annealing
```{r}
cat(paste(
    'Are they equal?',
    paste(all.equal(cpp_out[['bobyqa']]$no_anneal, R_out[['bobyqa']]$no_anneal),
    collapse = '\n'),
    sep = '\n'))
```




